---
title: "Statistical inference course project part I"
author: "Halley Wang"
date: "October 25, 2015"
output: pdf_document
---

        This report shows the relationship between the theoritical mean and variance with the sample mean and variance. By which it illustrates the nature of central limit theorem.

```{r load package, results = "hide"}
## Loading the necessary packages
library(ggplot2)
library(dplyr)
```

```{r parameters, cache = TRUE}
## Initialize the sample size, times of simulations and parameters for lambda:
sampleSize = 40
n = 1000
lambda = 0.2

## For controlling the random variables:
set.seed(123)
```

```{r sampling, cache = TRUE}
ExpDisSample = function(size = sampleSize, rate = lambda) {
        smpl = rexp(n = size, rate = rate)
        return (smpl)
}
```

        This process generates a sample with 40 observations.

```{r stimulation, cache = TRUE}
## make n times of stimulation:
ExpDisMeanStimulation = numeric()
for (i in 1:n) {
        ExpDisMeanStimulation = c(ExpDisMeanStimulation, mean(ExpDisSample()))
}

## Convert into a dataframe
ExpDisStimulation = data.frame(mean = ExpDisMeanStimulation)
head(ExpDisStimulation, 10)
```

        This process simulates 1000 replication of sample with 40 observation by repeating the process above.

```{r sample mean and variance, cache = TRUE}
## Calculate the sample mean and sample variance:
sampleMean = mean(ExpDisStimulation$mean)
sampleVariance = var(ExpDisStimulation$mean)
```

        We know that the random variable has mean lambda^-1 = `r lambda^-1`, while the sample variance is lambda^-2 = `r lambda^-2`. Due to the Central limit Theorem, we know that the sample should has same mean `r lambda^-1`, variance `r lambda^-2`/sqrt(`r sampleSize`) = `r lambda^-2/sampleSize`.
        In comparison, the sample mean is `r sampleMean`, the sample variance is `r sampleVariance`.


```{r histogram, cache = TRUE}
## Create ggplot object:
g1 = ggplot(data = ExpDisStimulation, aes(x = mean))

## Filling colors and 
g1 + geom_histogram(binwidth = 0.1, aes(fill = ..count..)) + geom_vline(x = c(lambda^-1, mean(ExpDisStimulation$mean)), color = c("GREEN", "RED"))
```

        As we can see from the graph, the sample mean distribution is roughly Gaussian, which agrees on the central limit theorem.
        The Green line represents the theoritical mean, while the red represents the sample mean. As we can see, they are converging to each other.